Acceleration of Global Search by Implementing Dual Estimates for Lipschitz Constant\thanks{This research was supported by the the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-08-29 2019/NUMTA_Barkalov/LNCS/numta19.tex
Correct all reviewers comments in Russian

This method of computing the characteristic is substantiated as follows. 
Let current minimum value of $z^*$ from (\ref{z}) be achieved at the left point of the $i^{\rm th}$ interval, i.e. $z^* = z_{i-1}$. Then, according to the rule (\ref{R}) the following inequality will be true: 
\[
R(i) \geq \Delta_i \left( 1 - \frac{1}{r} \right)^2.
\]
Consequently, two lower estimates of the two characteristics of current best interval $R_{loc}(i)$ and $R_{glob}(i)$ calculated with different parameters $r_{loc}$ and $r_{glob}$ will take different values.
However, if the former is multiplied by the coefficient $\rho$ from (\ref{pho}), the lower estimates of the characteristics of the best interval would match each other that would make the characteristics calculated for other intervals comparable as well.

@@

%Russian
Численное сравление алгоритмов было выполнено посредством решения нескольких серий задач, порожденных генератором GKLS \cite{Gaviano2003}. Данный генератор многоэкстремальных функций широко используется для сравнения методов глобальной оптимизации (see, for example, \cite{Barkalov2018,Paulavicius2014,Sergeyev2015}). В данном исследовании были решены шесть серий по 100 задач размерностей $N = 3,4,5$. Для каждой размерности генерировались \textit{Simple} and \textit{Hard} problems, отличающиеся размерами attraction region локальных и глобального minimizer.
Задача считалась решенной, если метод проводил очередное испытание в точке $y^k$, которая находилась в $\delta$-октрестности global minimizer $y^\ast$, 
т.е. $\left\|y^k-y^\ast\right\| <\delta\left\|b-a\right\|$, где  $a$ and $b$ --- границы search domain $D$.

The numerical comparison of the algorithms has been carried out using the GKLS test problem generator \cite{Gaviano2003}. This generator of multiextremal functions is often used for the investigations of the global optimization algorithms ~\cite{Barkalov2018,Paulavicius2014,Sergeyev2015}. Six GKLS classes of 100 differentiable test functions of the dimensions $N = 3,4,5$ have been used. For each dimension, both \textit{Hard} and \textit{Simple} classes have been considered. The difficulty of a class was increased either by decreasing the radius of the attraction region of the global minimizer, or by decreasing the distance from the global minimizer $y^\ast$ to the domain boundaries. The global minimizer $y^\ast$ was considered to be found, if the algorithm generated a trial point $y^k$ in the vicinity of the global minimum, i.e. $\left\|y^k-y^\ast\right\| <\delta\left\|b-a\right\|$, $a$ and $b$ are the boundaries of the search domain $D$.

>>>>

This method of computing the characteristic is substantiated as follows. 
%Russian
На каждой итерации будет возникать интервал, на одной из границ которого достигается текущее минимальное значение $z^*$ from (\ref{z}). Причем на заключительной фазе поиска данный интервал будет соответствовать интервалу, содержащему глобальный минимум, т.е. будет являться лучшим с точки зрения проведения дальнейших испытаний в нем.

Let current minimum value of $z^*$ from (\ref{z}) be achieved at the left point of the $i^{\rm th}$ interval, i.e. $z^* = z_{i-1}$. Then, according to the rule (\ref{R}) the following inequality will be true: 
\[
R(i) \geq \Delta_i \left( 1 - \frac{1}{r} \right)^2.
\]
Следовательно, для нижних оценок характеристик $R_{loc}(i)$ and $R_{glob}(i)$ calculated with different parameters $r_{loc}$ and $r_{glob}$, будет выполняться соотношение
\[
	\Delta_i \left( 1 - \frac{1}{r_{glob}} \right)^2 > \Delta_i \left( 1 - \frac{1}{r_{loc}} \right)^2.
\]

Таким образом, если выбирать наибольую из характеристик в соответствии с
\[
R(i) = \max\{R_{loc}(i),R_{glob}(i)\}
\]
то, как правило, будет выбираться характеристика $R_{glob}(i)$, соответствующая большей оценке Lipschitz constant; меньшая оценка (ускоряющая процесс уточнения текущего решения) использоваться не будет.
Однако если домножить нижнюю оценку для характеристики $R_{loc}(i)$ на коэффициент $\rho$ в соответствии с (\ref{pho}), то указанные нижние оценки будут равны, что сделает более вероятным выбор характеристики $R_{loc}(i)$, соответствующей меньшей оценке Lipschitz constant.

%Consequently, two lower estimates of the two characteristics of current best interval $R_{loc}(i)$ and $R_{glob}(i)$ calculated with different parameters $r_{loc}$ and $r_{glob}$ will take different values. However, if the former is multiplied by the coefficient $\rho$ from (\ref{pho}), the lower estimates of the characteristics of the best interval would match each other that would make the characteristics calculated for other intervals comparable as well.

@@

%Russian
Численное сравление алгоритмов было выполнено посредством решения нескольких серий задач, порожденных генератором GKLS \cite{Gaviano2003}. Данный генератор of multiextremal functions широко используется для сравнения методов глобальной оптимизации (see, for example, \cite{Barkalov2018,Paulavicius2014,Sergeyev2015}). В данном исследовании были решены шесть серий по 100 задач размерностей $N = 3,4,5$. Для каждой размерности генерировались \textit{Simple} and \textit{Hard} problems, отличающиеся размерами attraction region локальных и глобального экстремума.
Задача считалась решенной, если метод проводил очередное испытание в точке $y^k$, которая находилась в $\delta$-октрестности global minimizer $y^\ast$, 
т.е. $\left\|y^k-y^\ast\right\| <\delta\left\|b-a\right\|$, where  $a$ and $b$ --- границы search domain $D$.

%The numerical comparison of the algorithms has been carried out using the GKLS test problem generator \cite{Gaviano2003}. This generator of multiextremal functions is often used for the investigations of the global optimization algorithms ~\cite{Barkalov2018,Paulavicius2014,Sergeyev2015}. Six GKLS classes of 100 differentiable test functions of the dimensions $N = 3,4,5$ have been used. For each dimension, both \textit{Hard} and \textit{Simple} classes have been considered. The difficulty of a class was increased either by decreasing the radius of the attraction region of the global minimizer, or by decreasing the distance from the global minimizer $y^\ast$ to the domain boundaries. The global minimizer $y^\ast$ was considered to be found, if the algorithm generated a trial point $y^k$ in the vicinity of the global minimum, i.e. $\left\|y^k-y^\ast\right\| <\delta\left\|b-a\right\|$, $a$ and $b$ are the boundaries of the search domain $D$.
